---
title: "R markdown for reproducible research"
author: "AF"
date: "August 15, 2017"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## R Markdown

Read in dataset

```{r}
activity <- read.csv(file = "activity.csv", header = TRUE)

```

Making a plot of the total number of steps per day


```{r activity, echo=FALSE}
hist(activity$steps)
```

Mean and median number of steps taken each day
```{r}
library("dplyr")
meansteps <- aggregate(steps ~ date, data = activity, FUN = mean, rm.na=TRUE)
meansteps
aggregate(steps ~ date, data = activity, FUN = median, rm.na=TRUE)

```

Time series plot of average number of steps taken
```{r, echo = TRUE}
stepsinterval <- aggregate(steps~interval, data =activity, FUN =mean)
plot(stepsinterval, type = "l")

```

Finding the 5 minute interval that contains the maximum number of steps on average
```{r}
stepsinterval[which.max(stepsinterval$steps),]

```

Code to describe and impute missing data -- number of missing step values
```{r}
sum(is.na(activity$steps))

```

Replacing the NA step values with overall mean
```{r}
activity$steps[is.na(activity$steps)] <- mean(activity$steps, na.rm = TRUE)

```

Histogram of the total number of steps after the values are imputed
```{r}
hist(activity$steps)
```
 
Panel plot comparing the average number of steps taken per 5-minute interval across weekdays and weekends
```{r}
activity$weekday <- weekdays(as.Date(activity$date, "%Y-%m-%d"))
weekend <- filter(activity, weekday == "Saturday" | weekday == "Sunday")
weekday <- filter(activity, weekday != "Saturday" & weekday != "Sunday")
stepsweekend <- aggregate(steps~interval, data =weekend, FUN =mean)
stepsweekday <- aggregate(steps~interval, data =weekday, FUN =mean)
par(mfrow =c(2,1))
plot(stepsweekend, type = "l")
plot(stepsweekday, type = "l")

```


